Create data sets for modeling

### 2016-07-27 portfolio/analysis/3-createData_linear_modeling.Rmd
re-ran data creation file
included previous days

cfecAnnual$permit.prev = cfecAnnual$permit[idx]
cfecAnnual$ngear.prev = cfecAnnual$ngear[idx]
cfecAnnual$nspec.prev = cfecAnnual$nspec[idx]
cfecAnnual$npermit.prev = cfecAnnual$npermit[idx]
cfecAnnual$revenue.prev = cfecAnnual$revenue[idx]
cfecAnnual$specdiv.prev = cfecAnnual$specDiv[idx]
cfecAnnual$geardiv.prev = cfecAnnual$gearDiv[idx]
cfecAnnual$strategy.prev = cfecAnnual$strategy[idx]
cfecAnnual$strategy_gear.prev = cfecAnnual$strategy_gear[idx]
cfecAnnual$strategy_permit.prev = cfecAnnual$strategy_permit[idx]
cfecAnnual$weight.prev = cfecAnnual$weight[idx]
cfecAnnual$days.prev = cfecAnnual$days[idx]
```

>>>>

cfecAnnual$permit.prev = cfecAnnual$permit[idx]
cfecAnnual$ngear.prev = cfecAnnual$ngear[idx]
cfecAnnual$nspec.prev = cfecAnnual$nspec[idx]
cfecAnnual$npermit.prev = cfecAnnual$npermit[idx]
cfecAnnual$revenue.prev = cfecAnnual$revenue[idx]
cfecAnnual$specdiv.prev = cfecAnnual$specDiv[idx]
cfecAnnual$geardiv.prev = cfecAnnual$gearDiv[idx]
cfecAnnual$strategy.prev = cfecAnnual$strategy[idx]
cfecAnnual$strategy_gear.prev = cfecAnnual$strategy_gear[idx]
cfecAnnual$strategy_permit.prev = cfecAnnual$strategy_permit[idx]
cfecAnnual$weight.prev = cfecAnnual$weight[idx]
cfecAnnual$days.prev = cfecAnnual$days[idx]
cfecAnnual$days_permit.prev = cfecAnnual$days_permit[idx]
```
